### 2014-10-17 fundamentals/intro.tex
motivation

Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem, but existing tools are not sufficiently 
multi-scale. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming. 
However, an extensible architecture and discrete object tracking allow 
the creation and exchange ability of custom \Cyclus archetypes at any level of fidelity.

@@

The encapsulated plug-in architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle facility processes independent of the simulation 
logic. This design choice achieves two things. First, analysts across 
institutions can take advantage of the simulation logic \gls{API} and 
archetype ecosystem when they apply \Cyclus to their specific problem. The effort they 
undertake can thereby be focused on creating or customizing 
nuclear facility, institution, resource, and toolkit models within their 
specific area of expertise.

@@

We expect that there are a number of types of users and developers who will 
interact with the \Cyclus framework. National laboratory researchers,
graduate student and faculty researchers  Those people fall into a number of 
categories. All such people benefit from the modular architecture.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it takes advantage of modern computing resources. 
Furthermore, agent-based modeling provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
and a separate agent with fuel fabrication-related logic.

@@

One example use case seeks to capture system vulnerability to nefarious 
material diversion. This type of analysis requires discrete simulation of a 
target facility and the individual materials modified within it and is only 
achievable with discretely-modeled objects like those in the \Cyclus simulator.

>>>>

Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem, but existing tools are not sufficiently 
multi-scale. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels challenging within a single tool. 
However, an extensible architecture and discrete object tracking allow 
the creation and exchange ability of custom \Cyclus archetypes at any level of fidelity.

@@

The architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This `encapsulated,' `plug-in'
design choice achieves two things. First, analysts across 
research institutions can take advantage of the simulation logic \gls{API} and 
archetype ecosystem when they apply \Cyclus to their specific problem. This 
extensibility, magnified by an open source development process, frees the 
community of users to contribute desired features independen from the team of 
\Cyclus core developers. This mend-and-extend 
paradigm, common in modern software development, reduces maintenance overhead 
and improves code robustness \cite{citation_needed}. Finally, the researcher 
can therefore focus on creating or customizing 
nuclear facility, institution, resource, and toolkit models within their 
specific area of technical expertise.

@@

We expect that there are a number of types of users and developers who will 
interact with the \Cyclus framework. National laboratory researchers,
academic researchers, private-industry economic forcasters, and even students. 
in engineering courses will benefit from the ease of development and ease of 
customization provided by the modular architecture of \Cyclus.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it takes advantage of modern computing resources.  
Furthermore, agent-based modeling provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
and a separate agent with fuel fabrication-related logic. In the \Cyclus 
agent-based context, defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bonafide actors in the simulation. The two archetype libraries, therefore, need 
not have any shared knowledge of one another for them to be building blocks in 
the same simulation.

@@

One example use case seeks to capture system vulnerability to nefarious 
material diversion. This type of analysis requires discrete simulation of a 
target facility and the individual materials modified within it. 
Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies. 
Material risk analysis, therefore, demands discretely modeled objects like those 
in the \Cyclus simulator.
